### 2019-10-11 paper/methods.tex

\subsection{Fuel composition}
The general composition of the liquid fuel salt in this work is 70LiF - 
17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (misture of 
thorium and other actinides). The aim of this paper is to simulate the  
operation of \gls{SD-TMSR} for 60 years with different startup fissile 
compositions and without any external feed of fissile $^{233}$U which we 
assumed is unavailable. For that reason, five different types of initial 
fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF were 
considered:
\begin{enumerate}[label=(\alph*)]
	\item low-enriched uranium (LEU) (19.79\%);
	\item Pu mixed with \gls{LEU} (19.79\%);
	\item Pu reactor-grade \cite{marka1993explosive};
	\item transuranic (TRU) elements from LWR SF \cite{de2000scenarios};
	\item $^{233}$U for comparison purpose \cite{ashraf2019whole_core}.
\end{enumerate}

>>>>

\subsection{Fuel composition}
The general composition of the liquid fuel salt in this work is 70LiF - 
17.5BeF$_2$ - 12.5(HM)F$_4$ mole\%, where HM is the heavy metal (mixture of 
thorium and other actinides). The aim of this paper is to simulate the  
operation of \gls{SD-TMSR} for 60 years with different startup fissile 
compositions and without any external feed of fissile $^{233}$U which we 
assumed is unavailable. For that reason, five different types of initial 
fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF were 
considered:
\begin{enumerate}[label=(\alph*)]
	\item low-enriched uranium (LEU) (19.79\%);
	\item Pu mixed with \gls{LEU} (19.79\%);
	\item Pu reactor-grade \cite{marka1993explosive};
	\item transuranic (TRU) elements from LWR SF \cite{de2000scenarios};
	\item $^{233}$U for comparison purpose \cite{ashraf2019whole_core}.
\end{enumerate}
